IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-07-08 paper/real.tex
wip external

\Red{LOCK:deian}
While the described system implements |specLangJS seqf|, server-side
applications may require access to the file system, HTTP server, HTTP
client, etc.
%
Unfortunately, our formalism does not capture such external effects
and exposing the Node.js libraries directly to sandboxed tasks is unsafe.
%
Hence, we instead implement libraries such as the file system as
message exchanges between the sandboxed tasks (e.g., \textsf{task-1}
in Figure~\ref{fig:node}) and main Node.js task taht 
%
This is in part because how external effects 
%
Hence, our implementation of l
%This is, in part, because the handling of such effect

>>>>

\Red{LOCK:deian}
While the described system implements |specLangJS seqf|, server-side
applications may require access to the file system, HTTP server, HTTP
client, etc.
%
Unfortunately, our formalism does not capture such external effects
and exposing the Node.js libraries directly to sandboxed tasks is unsafe.
%
We, instead, implement libraries such as a labeled file system as
message exchanges between the sandboxed tasks (e.g., \textsf{task-1}
in Figure~\ref{fig:node}) and the main Node.js task that implements
our IFC monitor.\footnote{
  Importantly, our libraries provide mostly-identical interfaces to
  the standard Node.js libraries, hiding the underlying
  message-passing implementations.
}
%
This task is trusted to ensures that, for instance, labels are
propagated to files and that tasks are tainted when reading sensitive
files, as to preserve non-interference.
%
\Red{go into how this is app specific and it's not a huge limitation
  that our system does not capture this; e.g., even for fs semantics
  can vary: are labels serialized or not. later let's us change policy
more easily, the other is better for persistence}
